Aa Language Reference Manual

### 2014-08-10 v2/Ahir-asm/devel/docs/AaLRM.tex
Get github into synch.

Expressions in \Aa fall into the following classes
\begin{itemize}
\item Constant literal references.
\item Simple object references.
\item Indexed object references.
\item Pointer de-reference expressions.
\item Address-of expressions.
\item Unary expressions.
\item Binary expressions.
\item Ternary expressions.
\end{itemize}

@@

@@

These are of the
form
\begin{verbatim}
(<expression> <operation-id>  <expression>)
\end{verbatim}
The following binary operations are supported
\begin{verbatim}
// arithmetic operators
PLUS              + 
MINUS             - 
MUL               * 
DIV               / 
SHL               <<
SHR               >>

>>>>

Expressions in \Aa fall into the following classes
\begin{itemize}
\item Constant literal references.
\item Simple object references.
\item Indexed object references.
\item Pointer de-reference expressions.
\item Address-of expressions.
\item Unary expressions.
\item Slice expressions.
\item Bitmap (bit permutation) expressions.
\item Binary expressions.
\item Ternary expressions.
\end{itemize}

@@

\subsection{Slice expressions}

Slice expressions can be used to extract a contiguous
bit-field from a value.  They have the
following syntax:
\begin{verbatim}
LPAREN $slice <expression> <high-index> <low-index> RPAREN
\end{verbatim}
where high-index and low-index are constant non-negative
integers.  The result of executing the expression is
an unsigned integer whose width is $(high-index - low-index)+1$.
The value produced by expression may be of any type, but
for the slicing, it is flattened in the natural manner
(see the notes about aggregate types).  All bit-vectors
are assumed to indexed as $HIGH$ dowto $LOW$.

For example
\begin{verbatim}
( $slice ($bitcast ($uint<16>) _h1234) 8 4) = _h3
\end{verbatim}

\subsection{Bitmap expressions}

These expressions can be used to express bit permutations
in a word.  The syntax is as follows
\begin{verbatim}
LPAREN $bitmap <expression> ( <from-index> <to-index> )+ RPAREN
\end{verbatim}
The flattened bit-vector value of expression is permuted according
to the information provided by the $(from,to)$ pairs (result(to) = source(from)).

For example
\begin{verbatim}
( $slice ($bitcast ($uint<4>) _h3) 0 3 1 2 2 1 3 0 ) = _he
\end{verbatim}

@@

These are of the
form
\begin{verbatim}
(<expression> <operation-id>  <expression>)
\end{verbatim}
The following binary operations are supported
\begin{verbatim}
// arithmetic operators
PLUS              + 
MINUS             - 
MUL               * 
DIV               / 
SHL               <<
SHR               >> 
ROL               <o<
ROR               >o>
